Summary Tables ITHIMR

### 2019-05-03 summary_tables_PA_AP.Rmd
added striking vehicles

cities<- names(io)
cities<- cities[-2]

@@

>>>>

cities<- names(io)
cities<- cities[-c(1,2)]

@@

# Striking vehicles in scenarios

scenarios<- c('Baseline', 'Scenario 1', 'Scenario 2', 'Scenario 3', 'Scenario 4', 'Scenario 5')
for (i in 1: length(scenarios))
{
whw<-as.data.frame(rowSums(io[[cities[x]]]$outcomes$whw[[scenarios[i]]]$whw))
noov<-as.data.frame(rowSums(io[[cities[x]]]$outcomes$whw[[scenarios[i]]]$noov))
names(whw)[1]<- as.character(scenarios[i])
names(noov)[1]<-as.character(scenarios[i])

if (i ==1 )
{
 summary<-round(rbind(whw,noov), digits = 1)
} 
else
{
summary<- cbind(summary, round(rbind(whw, noov), digits=1) ) 
}

print (as.character(cities[x]))
print(summary)
